\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\usepackage{enumitem, hyperref}

\name{Mark Piraino} % Your name
%\address{\href{https://sites.math.northwestern.edu/~mpiraino}{https://sites.math.northwestern.edu/~mpiraino}} % Your address
\address{\href{mailto:mark.piraino@northwestern.edu}{mark.piraino@northwestern.edu}} % Your phone number and email

\begin{document}
	
\begin{rSection}{Academic appointments}
	
	{\bf RTG Postdoctoral fellow} \hfill {\em September 2019 - present} \\ 
	Northwestern University
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
{\bf University of Victoria} \hfill {\em August 2019} \\ 
Ph.D. in Mathematics
	
{\bf DePaul University} \hfill {\em June 2015} \\ 
M.S. in Pure Mathematics (with distinction)	

{\bf DePaul University} \hfill {\em June 2014} \\ 
B.S. in Chemistry and Mathematics 

\end{rSection}

\begin{rSection}{Certificates}
	{\bf Northwestern University School of Professional Studies} \hfill {\em December 2020 (expected)} \\ 
	Data Science and Visualization
\end{rSection}

\begin{rSection}{Research Interests}
	I am interested in a variety of problems most of which sit at the intersection of ergodic theory, dynamical systems, probability, and statistical mechanics. These include topics such as random matrix products, factor maps, sub-additive thermodynamic formalism, ergodic properties of equilibrium states, and phase transitions.
\end{rSection}

\begin{rSection}{Publications}
	\begin{itemize}
		\item 
		Transfer operators and limit laws for typical cocycles. (joint with Kiho Park)\\
		\emph{submitted}, ArXiv: \href{https://arxiv.org/abs/2007.02349}{\small{https://arxiv.org/abs/2007.02349}}
		
		\item 
		Single site factors of Gibbs measures.\\
		\emph{Nonlinearity}, DOI: \href{https://doi.org/10.1088/1361-6544/ab5179}{\small{https://doi.org/10.1088/1361-6544/ab5179}}
		
		\item 
		The weak Bernoulli property for matrix Gibbs states.\\
		to appear in \emph{Ergodic Theory and Dynamical Systems}, DOI: \href{https://doi.org/10.1017/etds.2018.129}{\small{https://doi.org/10.1017/etds.2018.129}}
		
		\item 
		Projections of Gibbs states for H\"older potentials.\\
		\emph{Journal of Statistical Physics}, DOI: \href{https://doi.org/10.1007/s10955-018-1967-3}{\small{https://doi.org/10.1007/s10955-018-1967-3}}
	\end{itemize}
\end{rSection}

\begin{rSection}{Teaching experience}
	\begin{rSubsection}{Northwestern University}{}{}{}
		\item
		Math 220-1: Single-Variable Differential Calculus. (Fall 2019 $\times 2$)
		
		\item
		Math 220-2: Single-Variable Integral Calculus. (Winter 2020, Fall 2010 $\times 2$)
		
	\end{rSubsection}
	%------------------------------------------------
	
	\begin{rSubsection}{University of Victoria}{}{}{}
		\item 
		Sessional instructor: Math 100 Calculus 1.
		
		\item 
		Tutorial leader: Math 100/101 Calculus, Math 110 Linear Algebra, Math 200 Multivariable Calculus.
		
		\item 
		Assistance center tutor: Informal drop in tutoring for 100/200 level mathematics courses.
	\end{rSubsection}
	
	\begin{rSubsection}{DePaul University}{}{}{}
		\item
		Teaching assistant: MAT 335-336 Real analysis I-II, MAT 150-152 Calculus I-III, MAT 304 Differential Equations.
	\end{rSubsection}
	
\end{rSection}


\begin{rSection}{Invited Talks}

\begin{itemize}
	\item 
	\emph{Matrix equilibrium states} \hfill January 2020\\
	JMM: Special session on Symbolic Dynamics, Denver CO
	
	\item 
	\emph{Matrix equilibrium states} \hfill July 2019\\
	Thermodynamic Formalism: Ergodic Theory and Geometry. Warwick, UK.
	
	\item 
	\emph{Single site factors of $g$-measures} \hfill August 2018\\
	50 years of Thermodynamic formalism. Leiden, Netherlands.
	
	\item 
	\emph{1-Block factors of $g$-measures} \hfill July 2018\\
	Topics in Mathematical Physics Satellite to the ICM 2018. S\~ao Paulo, Brazil.
	
\end{itemize}

\end{rSection}


\begin{rSection}{Awards and Scholarships}

\begin{itemize}
	\item 
	Governor General's gold medal. This is a university wide award given each year to one graduate student for the most outstanding thesis.
	
	\item
	Scholarships: DePaul Scholarship, Welch Scholarship, Graduate Assistantship (DePaul University), UVIC Outstanding Graduate Entrance (2015-2016), UVIC Graduate award (2015-2016, 2018-2019), UVIC Graduate Fellowship (2016-2017).
\end{itemize}

\end{rSection}


\end{document}
